--
title: "data_camp_pres"
output: html_document
---
Changing directory
```{r}
setwd("/nfs/mangrovesglobalization-data") # this connects our cloudbase folder with R 
```

Creating a shortcut
```{r}
 file.symlink(
     from = '/nfs/mangrovesglobalization-data',
     to = 'data'
 )
```


```{r}
library(tidyverse)
library(sf)
library(here)
library(rgdal)
library(spData) # Datasets for Spatial Analysis

```
The sf package is meant to supersede sp, implementing ways to store spatial data in R that integrate with the tidyverse workflow of the packages.

 - us_states    <- US states polygons
 - world        <- World country polygons
```{r}
#install.packages("sp")
library(sp)
```

```{r}
library(rnaturalearth)
```


```{r}
plot(ne_countries())
```

Load our data
```{r}
topGBEI<-read.csv("data/GBEI/top15GBEI.csv", header=TRUE, na.strings="")

```


```{r}
world<-world%>%
  rename(country=name_long)
```


```{r}
# ...... merge your data to sp/sf -----------------------------------------

names(topGBEI)    ## your results
class(topGBEI)

class(world) ## spatial map with boudary
names(world)

indicator  <- semi_join(x = topGBEI, 
                             y = world, 
                             by="country")
 
```

```{r}
indicator2<-indicator %>% 
  group_by(country) %>% 
  mutate(mean_ind=mean(as.numeric(as.character(overall)),na.rm=TRUE)) %>% 
           select(country,mean_ind) %>% 
           distinct()

```

```{r}
indicator2
```
```{r}
#we created a new simple feature object to give spatial component to indicator 2
sp_ind <- full_join(world,indicator2, by="country")
```

##The winner plot code!!

```{r}
ggplot(data=sp_ind)+
  geom_sf()+
  geom_sf(aes(fill=mean_ind))
```


```{r}
ggplot(data=sp_ind)+
  geom_sf()+
  geom_sf(aes(fill=mean_ind))+ggtitle("Global Biodiversity Engagement Index (GBEI) \n Data for Top Mangrove-Holding Countries")+ theme(plot.title = element_text(hjust =0.5))+ labs(fill = "GBEI")



```

